\section{Team members}
\begin{longtable}
    {|m{0.3\linewidth}|m{0.2\linewidth}|m{0.4\linewidth}|}
            \hline
            \textbf{Full name} & \textbf{Person code} & \textbf{Contact info}\\
            \hline
            \endhead
                Hessam Hashemizadeh & 10900041 & hessam.hashemizadeh@mail.polimi.it \\
            \hline
                Virginia Longo & 10685398 & virginia.longo@mail.polimi.it \\
            \hline
                Mobina Mahdavi & 10947943 & mobina.mahdavi@mail.polimi.it \\
            \hline
                Filippo Ranieri Pantaleone & 10664253 & filippo.pantaleone@mail.polimi.it \\
            \hline
            \caption{Members details}
            \label{table:mem_details}
\end{longtable}

All the team members of this group are enrolled in the Computer Science Engineering program.

\section{Purpose of the document}
This document presents the steps taken by our group, The Hive, to thoroughly evaluate a website by behaving as expert reviewers. We used two different methods (Inspection evaluation and User Testing), which we will present later.

\pagebreak

\section{Workflow of project activities}
The overall main task of Usability Evaluation has been divided into the following phases:

\begin{itemize}
	\item Agreement on the heuristics and scale to use;
	\item Inspection evaluation;
	\item Analysis of the results and preparation of for the following phase;
	\item User Testing;
	\item Analysis of the results and comparison.
\end{itemize}

\section{Abstract}
In this report we present the execution steps and the results of the evaluation of the UNICEF website (\url{www.unicef.org}) for the Hypermedia Applications 2023-2024 Inspection project. The tasks were to execute an Inspection of the website by ourselves and then compare the results with those of the second phase, User Testing, where other users would complete a series of tasks and comment on. Both phases' results suggested that the website has critical issues that prevent users from being able to access the resources they need due to design and usability problems. We noticed though that such issues were less critical with respect to people with no technical knowledge/background, who were able to complete their tasks more easily and quickly. We then provided a set of recommendations to improve the usability of the website.
